\section{Game Manual - Welcome to Cells!}

Welcome to Cells, and thank you for participating in this test. The game is in early development for a university project, which is why your feedback is extremely important. The following manual will describe the game's features and hopefully give you a better understanding of what it is you can achieve in Cells.

\subsection{Your Objective}

Your goal is to beat the other cell on the board. Your cell is green, and the enemy cell is red. It is a game of algorithmic thinking, so you will have to write some sort of algorithm, that solves your task. Consider an algorithm to be a set of instructions - such as a recipe, when you are cooking a meal. It will likely take more than one play through to win the game!

\subsection{Strengthen Your Cell}

By consuming stars, your energy level will rise, and when it reaches a point greater than your opponents, you are able to eat them up! But be careful, you spend energy on every action you make across the board, so it is important to stock up on energy (stars)!

\subsection{To start press singleplayer..}

You will find that some of the features are greyed out, this indicates what you cannot click on. To start up a new game simply chose \textbf{singleplayer} $->$ \textbf{skirmish} $->$ \textbf{new}.

\subsection{Welcome to the Editor}

The editor is where you create your cell's algorithm. Every hexagon dropped into the empty black fields, will be executed by the cell. When your cell has executed every action brought into the editor, it will start all over again, so your cell will never cease to do actions, unless directly specified not to.


\subsection{When you are done}

Press OK in the bottom right, this will start the game with the instructions you gave it in the editor. 


May the best cell win, and good luck!