\chapter*{Preface}

The following report is written as part of a semester project by five students from the Department of Computer Science at Aalborg University. The report is written in parallel with courses in Programming Paradigms, Data Intensive Systems, Agent Technologies, and Web Engineering. Not all students in the group have followed the same courses, and several mini projects in all of the courses have been a limiting factor in terms of time available to work on the project.\\

The report is structured as a classic analysis, design, implementation, testing and reflection report, even though the classic waterfall development method was not used. The report is written in such a way, that it should at least be understandable for students that have completed the $6^{th}$ semester in Software Engineering. We will try to introduce possible new concepts and definitions when they are first used in the report to make it more readable for the user.

\section*{Acknowledgments}

We would like to thank our guidance counselor Martin Leginus for providing comments on our report, direction in the project, and supply additional reading material for inspiration.
Additionally, we would like to thank our associate professor Kurt N{\o}rmark for allowing us to interview him about possible approaches for teaching programming constructs in terms of which paradigm to focus on based on the target group.
The interview provided us with documentation and argumentation for selecting the imperative paradigm as the base paradigm for our game.
Lastly, we would like to thank the participants, that have taken the time to test our game and give feedback.
The feedback provided is valuable in terms of possible further development, and it helps us learn more about designing games in general.
